---
title: "Workshop: Quantitative analysis of ChiP-seq, ATAC-seq, and related DNA enrichment assays"
author:
  - name: Rory Stark
    affiliation: Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge, UK
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteIndexEntry{QuantitativeChIPWorkshop}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  bookdown::html_document2: default
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_caption: true
    number_sections: true
    mathjax: null
editor_options:
    chunk_output_type: console
bibliography: DiffBind.bib
---

```{css, echo=FALSE}
.infobox {
  padding: 1em 1em 1em 4em;
  margin-bottom: 10px;
  border: 2px solid #008000;
  border-radius: 10px;
  background: #DCDCDC 5px center/3em no-repeat;
  color: #8B0000;
}
.center {
  text-align: center;
}
```

```{r, setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(out.width="100%", cache=TRUE)
knitr::opts_knit$set(root.dir="../inst/extdata")
```

# Quantitative analysis of ChiP-seq, ATAC-seq, and related DNA enrichment assays

## Workshop participation

Docker users can run this workshop locally via:

```
docker run -e PASSWORD=bioc -p 8787:8787 crukcibioinformatics/quantitative_chip_workshop:latest
```

## Requirements: R/Bioconductor packages

The workshop uses a Docker container with Bioconductor Release version `3.12`.
If you would like to install Bioconductor on your computer **at a later date**,
see the [Bioconductor installation](https://www.bioconductor.org/install)
instructions.

Here is a list of packages that we will be using:

```{r load}
library(DiffBind)
library(GreyListChIP)
library(csaw)
```

## Let's do a _DiffBind_  analysis!

### Set directory to where the data are
```{r showdir}
getwd()
list.files()
#setwd(system.file("doc",package="QuantitativeChIPseqWorkshop"))
#getwd()
#list.files("..")
#setwd("..")
#list.files()
#setwd("inst/extdata")
#list.files()
```


# rstudioapi::viewer("/usr/local/lib/R/site-library/QuantitativeChIPseqWorkshop/doc/Quantitative-ChIPseq-Workshop.html")






